\section{Task 3: Memo}
\begin{center}
    \Large\textbf{Recommendations for Sustainable Tourism in Juneau, Alaska}
\end{center}

{\small

Dear Tourist Council,

It is our great honour to present to you our recommendations for 
sustainable tourism in Juneau, Alaska. We have conducted a thorough 
analysis of the current situation in Juneau and have identified several key 
areas that need to be addressed in order to ensure the long-term sustainability 
of the tourism industry in the region. 
Our recommendations are based on the principles of sustainable tourism, 
which aim to balance the economic, social, and environmental impacts of tourism 
in order to ensure that it can continue to benefit both the local community and 
the environment for generations to come. Our approaches, findings and suggestions are as follows.

Firstly we summarized a general equation aiming to balance the economic, social, 
and environmental impacts of tourism. Then we looked into these aspects
and devised a model accordingly for each. \textit{SARIMAX, Linear-Regression} models 
were used to ensure the accuracy and reliability of our findings and suggestions.

Here are some findings based on our predictions.

\begin{itemize}
    \item The emission of carbon dioxide from tourism is increasing at an alarming rate, and it is 
    highly correlated with the square number of tourists.
\end{itemize}

Based on these findings, we put forward the following recommendations and measures.

\begin{itemize}
    \item \textbf{Economy}
    \item \textbf{Society}
    \item \textbf{Environment}
\end{itemize}

I hope you find our recommendations useful and that they will help to guide
the development of sustainable tourism in Juneau. We believe that by working
together, we can create a more sustainable future for the tourism industry in
the region. Thank you for your attention and consideration. Feel free to contact us for any further information.

\begin{flushright}
    Sincerely,\\
    Team \# 2503720 Members
    \end{flushright}

}

\clearpage